---
name: Tristan RH 
surname: Goodbody Ph.D.
position: "Remote sensing of forests researcher"
address: "University of British Columbia, Vancouver"
#profilepic: "./img/me.jpg"
phone: +604 992 1327
email: "goodbody.t@gmail.com"
github: tgoodbody
twitter: GoodbodyT
orcid: 0000-0002-6894-7925
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
docname: curriculum vitae
output: vitae::awesomecv
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)


pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )
library(magrittr)
# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) %>%
  invisible()

source(file = here("r","data.r"))

```

# About me

8 years experience and doctorate in remote sensing, machine learning and data fusion in the context of forest inventory and resources management. Collaborating with multiple levels in government, private industry and academia. Producing high impact science that continues to be operationalized. Mentoring students of all levels of post-secondary education in remote sensing, data science and forest management.

# Research Interests

\begin{cvskills}
  \cvskill
    {Forest Management}
    {Forest attribute mapping, forest mensuration \& sampling}

  \cvskill
    {Remote sensing}
    {Airborne lidar \& digital photogrammetric point clouds, drone-based datasets, sattellite imagery}
    
  \cvskill
    {Data science}
    {Predictive modelling, spatial data, reproducible science}
    
  \cvskill
    {Enhanced forest inventory}
    {Integrating remotely sensed data into forest management and planning frameworks}
    
  \cvskill
    {Ecosystem processes and function}
    {Vegetation structure, flora and fauna, disturbances \& climate change}
    
\end{cvskills}

# Experience

```{r Experience, results = "asis"}

experience %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where, .protect = F
  )

```
\pagebreak

# Education

```{r EDUCATION}
education %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where, .protect = F
  )

```

# Applied Skills

\begin{cvskills}

  \cvskill
    {Remote Sensing}
    {Forest attribute modelling, point cloud processing, digital aerial photogrammetry, drone data sets}

  \cvskill
    {Data Science}
    {R (Advanced), machine learning, image processing, ecological modelling, inventory analysis, software development}
    
  \cvskill
    {Collaboration}
    {International academic, government, and industry representatives}

  \cvskill
    {Writing}
    {Scientific publications, public reports, funding grants, reproducible reporting}
    
  \cvskill
    {Communication}
    {Confident public speaker, graduate student mentor, effective graphic design}  
    
\end{cvskills}

# Soft Skills

\begin{cvskills}
  \cvskill
    {Personal}
    {Accountable, adaptable, assertive, confident, dependable, diligent, enthusiastic, friendly, reliable, respectful, positive}

  \cvskill
    {Social}
    {Conflict resolution, emotionally \& culturally intelligent, equitable, leadership, inclusive, negotiation, team-building}
    
  \cvskill
    {Methodological}
    {Analytical, proactive, problem-solving, organized, time management, work ethic}
    
  \cvskill
    {Languages}
    {English/Spanish, German (basic)}
    
\end{cvskills}

# Awards

```{r AWARDS}

awards %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

# Peer-Reviewed Publications

\begin{cvskills}
  \cvskill
    {Google Scholar}
    {Total citations: 1135  , h-index: 17}
    
  \cvskill
    {Web of Science}
    {Total citations: 745  , h-index: 13}
    
\end{cvskills}

```{r JOUNRALARTICLES}
bib <- bibliography_entries("publications.bib") %>%
  arrange(desc(issued))

bib$`container-title` <- str_to_sentence(bib$`container-title`, locale = "en")

bib
  
```

# Software & Guides

```{r SOFTWARE}
bib <- bibliography_entries("software.bib")

bib
  
```

# Conferences

```{r PRESENTATIONS}

p <- presentations  %>%
    filter(detail == "Conference") %>%
    mutate(detail = NA)
    
p %>%
detailed_entries(
with = title,
what = unit,
why = detail,
when = glue::glue("{startMonth} {startYear}",.na = ""),
where = where, .protect = F
)

```

# Teaching & Instructional Workshop Experience

```{r TEACHING}

p <- presentations %>%
    filter(detail == "Workshop") %>%
    mutate(detail = NA)
    
p %>%
detailed_entries(
with = title,
what = unit,
why = detail,
when = glue::glue("{startMonth} {startYear}",.na = ""),
where = where, .protect = F
)

```

# International Journals

\begin{cvskills}
  \cvskill
    {Reviewer}
    {ISPRS Journal of Photogrammetry and Remote Sensing,  Forest Ecosystems,  Forestry Chronicle,  Remote Sensing  }
    
  \cvskill
    {Guest Editor}
    {Remote Sensing Special Issue: Aerial and Near-Field Remote Sensing Developments in Forestry}
    
\end{cvskills}