---
name: Tristan RH 
surname: Goodbody
position: "Remote Sensing of Forests Specialist"
address: "University of British Columbia, Vancouver"
#profilepic: "./img/me.jpg"
phone: +604 992 1327
email: "goodbody.t@gmail.com"
github: tgoodbody
twitter: GoodbodyT
orcid: 0000-0002-6894-7925
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
docname: CV
output: vitae::awesomecv
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)


pkgs <- c('vitae' ,'here' ,'tinytex' ,'tibble' ,'glue' ,'rmarkdown' ,'dplyr', 'readr' ,'yaml')
xfun::pkg_attach2(pkgs)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data sctructure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative Filepaths
             ,'readr'     # Data Loading
             ,'tidyverse' # Needed for bind_rows and whatever
             ,'scholar'   # Updating publications from google scholar
             ,'kableExtra'# Adding technicalskills table
            )
library(magrittr)
# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
lapply(packages, library, character.only = TRUE) %>%
  invisible()

source(file = here("r","data.r"))

```

# About me

I have 7 years of experience working with remote sensing data in the context of forest resources management and inventory. During that time I have successfully defended my PhD, collaborated with multiple levels of government, private industry, and academia, acted as a mentor for students of all levels of post-secondary education, and produced high impact science that continues to be operationalized. My work in developing a robust open-source tool for [structurally guided sampling ](https://tgoodbody.github.io/sgsR/) has received international and interdisciplinary acclaim and is being actively developed to continue to enhance forest inventories.

# Experience

```{r Experience, results = "asis"}

experience %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where, .protect = F
  )

```
\pagebreak

# Education

```{r EDUCATION}
education %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear} - {endMonth} {endYear}",.na = ""),
    where = where, .protect = F
  )

```

# Skills

\begin{cvskills}
  \cvskill
    {Data Science}
    {R (Advanced), LAStools, lidR, ENVI, ARC/QGIS, ArcPy, Developed sgsR package}

  \cvskill
    {Research}
    {Forest modelling, inventory analysis, lidar processing, digital aerial photogrammetry, raster \& vector analysis}
    
  \cvskill
    {Collaboration}
    {Extensive work with international academic, government, and industry representatives}

  \cvskill
    {Writing}
    {Scientific publications, public reports, funding grants, reproducible reporting (Rmarkdown, bookdown)}
    
  \cvskill
    {Communication}
    {Confident public speaker, effective graphic design (Illustrator/inDesign)}  

  \cvskill
    {Languages}
    {English/Spanish (bilingual)}
\end{cvskills}

# Awards

```{r AWARDS}

awards %>%
  detailed_entries(
    with = area,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

# Peer-Reviewed Publications

```{r JOUNRALARTICLES}
bib <- bibliography_entries("publications.bib") %>%
  arrange(desc(issued))

bib$`container-title` <- str_to_sentence(bib$`container-title`, locale = "en")

bib
  
```

# Presentations

```{r PRESENTATIONS}

presentations %>%
  detailed_entries(
    with = title,
    what = unit,
    why = detail,
    when = glue::glue("{startMonth} {startYear}",.na = ""),
    where = where, .protect = F
  )

```
